The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-12 manuscript/manuscript.Rnw
text cite yammamoto

The elephant is strikingly the only mammal analyzed that shows high
expression of the primarily pituitary hormone prolactin (PRL) in the
placenta. %
\DLA{This is totally not true. \textit{A. fusciceps} expresses PRL,
  and so does \textit{S. carmeli}, and \textit{B. taurus}, \textit{M.
    musculus}, all have expansions of prolatacin.}
%
All afrotherians yet analyzed contain only one prolactin
gene, and prolactin has undergone adaptive evolution on the elephant
lineage \cite{Wallis2009:ProlactininAfrotheriacharacterization}.
\cite{Yamamoto.ea2011:PlacentationinAfricanelephant} noted the
presence of a prolactin in the trophoblast of the elephant placenta
using immunohistological staining and human derived antibodies. A
previous analysis of the elephant placenta also detected the
expression of prolactin (Hou et al., 2012). Here we confirm that the
sole prolactin in the elephant is not only expressed but highly
expressed in the placenta, and likely functions both in the
maintenance of the corpus luteum and as a placental lactogen \cite{Yamamoto.ea2011:PlacentationinAfricanelephant}. PRL is not expressed in the opossum, even though there
is evidence that it is expressed in the placenta of another marsupial,
the tammar wallaby \cite{Menzies.ea2011:Placentalexpressionofpituitary}. This suggests that
placental prolactin expression in marsupials may be as diverse as in
eutherian mammals. Although, PRL is not expressed to any great degree
in the placenta other mammals, we see very high expression of genes
which resulted from duplications of PRL in both the cow \DLA{(Table X)}, as
well as mouse \DLA{(Supplemental Table X)}. \DLA{Describe these}

>>>>

The elephant is strikingly the only mammal analyzed that shows high
expression of the primarily pituitary hormone prolactin (PRL) in the
placenta. %
\DLA{This is totally not true. \textit{A. fusciceps} expresses PRL,
  and so does \textit{S. carmeli}, and \textit{B. taurus}, \textit{M.
    musculus}, all have expansions of prolatacin.}
%
All afrotherians yet analyzed contain only one prolactin
gene, and prolactin has undergone adaptive evolution on the elephant
lineage \cite{Wallis2009:ProlactininAfrotheriacharacterization}.
\citet{Yamamoto.ea2011:PlacentationinAfricanelephant} noted the
presence of a prolactin in the trophoblast of the elephant placenta
using immunohistological staining and human derived antibodies. A
previous analysis of the elephant placenta also detected the
expression of prolactin (Hou et al., 2012). Here we confirm that the
sole prolactin in the elephant is not only expressed but highly
expressed in the placenta, and likely functions both in the
maintenance of the corpus luteum and as a placental lactogen \cite{Yamamoto.ea2011:PlacentationinAfricanelephant}. PRL is not expressed in the opossum, even though there
is evidence that it is expressed in the placenta of another marsupial,
the tammar wallaby \cite{Menzies.ea2011:Placentalexpressionofpituitary}. This suggests that
placental prolactin expression in marsupials may be as diverse as in
eutherian mammals. Although, PRL is not expressed to any great degree
in the placenta other mammals, we see very high expression of genes
which resulted from duplications of PRL in both the cow \DLA{(Table X)}, as
well as mouse \DLA{(Supplemental Table X)}. \DLA{Describe these}
